Lichat, A Lightweight Chat Protocol

### 2022-01-24 els2022-lichat/paper.tex
Minor

Jennings et al.\cite{jennings2006study} compare a variety of Instant Messenger systems such as AIM and MSN, which are all now largely defunct. The ppaper focuses primarily on the distribution of sessions and the scalability of the networks. Lichat is explicitly focused on small to mid-sized communities and is thus not concerned with the scalability to tens of thousands of simultaneous users.

@@

\section{Acknowledgements}\label{acknowledgements}
We would like to thank Georgiy Tugai, Jan Moringe, and Selwyn Simsek for their feedback on this paper and contributions to Lichat's development.

>>>>

Jennings et al.\cite{jennings2006study} compare a variety of Instant Messenger systems such as AIM and MSN, which are all now largely defunct. The paper focuses primarily on the distribution of sessions and the scalability of the networks. Lichat is explicitly focused on small to mid-sized communities and is thus not concerned with the scalability to tens of thousands of simultaneous users.

@@

\section{Acknowledgements}\label{acknowledgements}
We would like to thank Georgiy Tugai, Jan Moringe, Bart Botta, and Selwyn Simsek for their feedback on this paper and contributions to Lichat's development.
